Signatures of Foreground Sky in Power Spectra of Redshifted Neutral Hydrogen from the Epoch of Reionization

### 2014-09-05 foreground_delay_spectrum_modeling.tex
added calibration description, simplified delay CLEAN description

\subsection{Data Analysis}\label{sec:data-analysis}
The data are flagged for interference cite ao, removing 3\% of the data.  averaged in time and frequency to 2s, 40khz

\subsection{Imaging and deconvolution}\label{sec:FHD}

{\bf Describe the FHD data analysis up to the point of getting calibrated visibilities here.}

@@

We obtain the delay spectrum of these calibrated visibilities using equation~\ref{eqn:delay-transform} while choosing $W'_f(f)$ to be a {\it Blackman--Harris} window function. Due to periodic gaps in frequency bandpass occurring in intervals of 1.28~MHz (see figure~\ref{fig:bandpass}), the delay spectrum is expected to contain harmonics of actual foreground emission repeated at intervals of 0.78~$\mu$s. Hence, we have employed deconvolution by {\it CLEAN} algorithm \citep{tay99} along the delay axis \citep{par09,par12} to rid the delay spectra of such artifacts. The convolving kernel for the algorithm is given by the inverse Fourier transform of the instrumental bandpass shape.

>>>>

\subsubsection{Initial Data processing}\label{sec:data-analysis}
The data are flagged\footnote{\url{http://sourceforge.net/p/aoflagger}} for interference, removing 3\% of the data and averaged in time  and frequency from the raw 1/2s,40kHz to 2s, 80khz. These data are then calibrated to a simulation of the sky containing 2420 point sources selected from the MWA Commissioning Survey (N.H Walker, in prep).  MWACS was compiled using observations taken with subsets of the array during the final buildout and commissioning. It has a flux limit of 25~mJy and a the declination range of -12\arcdeg to -40\arcdeg evenly covering the field of view of the observations reported here.        The calibration sources are selected to fall within the 10\% primary lobe of the tile beam. The calibration algorithm computes a per channel, per antenna, complex gain which flattens the bandpass and removes small phase slopes due to variation in cable delay. %possibly could add elaboration, if I knew exactly which version of the cal was done here. doesn't really matter

@@

We obtain the delay spectrum of these calibrated visibilities taking the delay transform of each baseline's spectrum (equation~\ref{eqn:delay-transform}) choosing $W'_f(f)$ to be a {\it Blackman--Harris} window function. The spectrum is multiplied by  the additional weight of the flagged channels which occur rarely for interference and at at regular spacing every 1.28~MHz where the edges of coarse channels are known to have a slight aliasing effect.  These weights translate into a convolution in the delay space by a ringing harmonic point spread function.  We deconvolve using a one dimensional CLEAN algorithm   \citep{tay99} as described for the delay axis by \citet{par09,par12}.
